\LARGE A double-sampling extension of the German National Forest Inventory for design-based small area regression estimation of timber volume resources on forest district levels \\ \vspace{2ex} \large Large scale application to the federal state of Rhineland-Palatinate \vspace{-1ex}

### 2018-02-03 Draft_Form/tex/Abstract.tex
update 03_02_2018
update 03_02_2018

\section*{Abstract} 
\label{sec:abstract}
The German National Forest Inventory consists of a systematic grid of permanent sample plots and provides a reliable evidence-based assessment of the state and the development of Germany's forests on national and federal state level in a 10 year interval. However, the data have scarcely been used for estimation on smaller management levels such as forest districts due to insufficient sample sizes within the area of interests and the implied large estimation errors. In this study, we present a double-sampling extension to the existing German National Forest Inventory (NFI) that allows for the application of recently developed design-based small area estimation procedures that try to overcome the restriction in terrestrial sample size by enlarging the sample by a large set of model predictions. We illustrate the implementation of the estimation procedure and evaluate its potential by the example of timber volume estimation on two small scale management levels (42 and 392 forest district units respectively) in the federal German state of Rhineland-Palatinate. A LiDAR derived canopy height model and a tree species classification map based on satellite data were used as auxiliary information in an ordinary least square regression model to produce the timber volume predictions on the plot level. The results indicate that the suggested double-sampling procedure can significantly increase estimation precision on both management levels compared to estimates based on the simple random sampling (SRS) estimator: on Forstamt-level, the proportion of estimation errors below 6\% could be increased from 10\% to 60\% (90\% were below 7\% estimation error). The increase of estimation precision was even more pronounced on the Revier-level, although the errors were generally higher than on the Forstamt-level: here, the proportion of estimation errors below 10\% could be increased from 15\% to 40\%. The average decrease in variance was ... and ..., and the relative efficiency was ... and ... on Forstamt and Revier-level respectively.

>>>>

\section*{Abstract} 
\label{sec:abstract}
The German National Forest Inventory consists of a systematic grid of permanent sample plots and provides a reliable evidence-based assessment of the state and the development of Germany's forests on national and federal state level in a 10 year interval. However, the data have yet been scarcely used for estimation on smaller management levels such as forest districts due to insufficient sample sizes within the area of interests and the implied large estimation errors. In this study, we present a double-sampling extension to the existing German National Forest Inventory (NFI) that allows for the application of recently developed design-based small area regression estimators. We illustrate the implementation of the estimation procedure and evaluate its potential by the example of timber volume estimation on two small scale management levels (45 and 405 forest district units respectively) in the federal German state of Rhineland-Palatinate. An airborne laserscanning (ALS) derived canopy height model and a tree species classification map based on satellite data were used as auxiliary data in an ordinary least square regression model to produce the timber volume predictions on the plot level.
The results support that the suggested double-sampling procedure can substantially increase estimation precision on both management levels: the two-phase estimators were able to reduce the variance of the SRS estimator by 43\% and 25\% on average for the two management levels respectively.

%The German National Forest Inventory consists of a systematic grid of permanent sample plots and provides a reliable evidence-based assessment of the state and the development of Germany's forests on national and federal state level in a 10 year interval. However, the data have yet been scarcely used for estimation on smaller management levels such as forest districts due to insufficient sample sizes within the area of interests and the implied large estimation errors. In this study, we present a double-sampling extension to the existing German National Forest Inventory (NFI) that allows for the application of recently developed design-based small area estimation procedures that try to overcome the restriction in terrestrial sample size by enlarging the sample by a large set of model predictions. We illustrate the implementation of the estimation procedure and evaluate its potential by the example of timber volume estimation on two small scale management levels (42 and 392 forest district units respectively) in the federal German state of Rhineland-Palatinate. A LiDAR derived canopy height model and a tree species classification map based on satellite data were used as auxiliary information in an ordinary least square regression model to produce the timber volume predictions on the plot level. The results indicate that the suggested double-sampling procedure can significantly increase estimation precision on both management levels compared to estimates based on the simple random sampling (SRS) estimator: on Forstamt-level, the proportion of estimation errors below 6\% could be increased from 10\% to 60\% (90\% were below 7\% estimation error). The increase of estimation precision was even more pronounced on the Revier-level, although the errors were generally higher than on the Forstamt-level: here, the proportion of estimation errors below 10\% could be increased from 15\% to 40\%. The average decrease in variance was ... and ..., and the relative efficiency was ... and ... on Forstamt and Revier-level respectively.

### 2018-02-03 Draft_Form/tex/Introduction(2).tex
update 03_02_2018
update 03_02_2018

The aim of this study was to investigate whether the German NFI data can provide acceptable estimation precision on two forest district levels when incorporated in small area estimation procedures. We therefore conducted a study in the German federal state Rhineland-Palatinate where we extended the German NFI to a double-sampling design and applied three types of design-based small area regression estimators in order to derive point and variance estimates of mean standing timber volume for 42 and 392 forest districts respectively. The SA-estimators we considered were the \textit{pseudo-small}, \textit{extended pseudo-synthetic} and the \textit{pseudo-synthetic} design-based small area estimator suggested by \citet{mandallaz2013a, mandallaz2013b}. Auxiliary information were obtained from a countrywide airborne Laser scanning (LiDAR) canopy height model (CHM) and a tree species classification map and used for regression within tree species strata. The estimation accuracies were compared to those achieved under SRS sampling. The chosen double-sampling estimators were favoured for several reasons: \textbf{(i)} the design-based frame considerably relaxes requirements on the regression model which seemed appropriate facing severe quality restrictions in the LiDAR data; \textbf{(ii)} the estimators can consider \textit{non-exhaustive}, i.e. non wall-to-wall, auxiliary information; \textbf{(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators; and \textbf{(iv)} the asymptotically unbiased g-weight variance accounts for the design-dependency of the regression coefficients on the sample (\textit{internal model approach}) and is also robust to heteroscedasticity of the model residuals.\par

>>>>

The aim of this study was to investigate whether the German NFI data can provide acceptable estimation precision on two forest district levels when incorporated in small area estimation procedures. We therefore conducted a study in the German federal state Rhineland-Palatinate where we extended the German NFI to a double-sampling design and applied three types of design-based small area regression estimators in order to derive point and variance estimates of mean standing timber volume for 45 and 405 forest districts respectively. The SA-estimators we considered were the \textit{pseudo-small}, \textit{extended pseudo-synthetic} and the \textit{pseudo-synthetic} design-based small area estimator suggested by \citet{mandallaz2013a, mandallaz2013b}. Auxiliary data were obtained from a countrywide airborne Laser scanning (LiDAR) canopy height model (CHM) and a tree species classification map and used for regression within tree species strata. The estimation accuracies were compared to those achieved under SRS sampling. The chosen double-sampling estimators were favoured for several reasons: \textbf{(i)} the design-based frame considerably relaxes requirements on the regression model which seemed appropriate facing severe quality restrictions in the LiDAR data; \textbf{(ii)} the estimators can consider \textit{non-exhaustive}, i.e. non wall-to-wall, auxiliary information; \textbf{(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators; and \textbf{(iv)} the asymptotically unbiased g-weight variance accounts for the design-dependency of the regression coefficients on the sample (\textit{internal model approach}) and is also robust to heteroscedasticity of the model residuals.\par

### 2018-02-03 Draft_Form/tex/Results.tex
update 03_02_2018
update 03_02_2018

On FA level,

% NOTES:
% - 1) address feasibility of estimations for each estimator
% - 2) give general overview about estimation results (see Breidenbach) before going into more detail
%

% Feasibility: 
% FA-level: for 44 out of 45 FA-units, the full model could be applied. For one remaining, only the model without tree species was applied.
% 
% FR-level: 
%
% mathemat. feasibility:
% - op-estimation feasible for 388 of the 405 fu-units. --> for 17 fus not possible due to n2G < 2
% - psmall / extpsynth possible for 386 of the 405 units (for 19 fus not possible). Reason: for 19 fus we have n2G < 2
% - psynth not possible for 403 of 405. For 2 units not possible due to n1G < 2 (these two are included in the 19 above).
%    -> basically, for these 2 fu-units, none of the estimators could produce estimations due to n1G < 2
%  
%  restriction of unbiased estimtors to n2G >= 4: 
% - psmall / extpsynth: 65 of the 386 fu-units have n2G < 4, so theyx cancel out. Thus we have 19 + 65 = 84 fu-units for which no psmall & extpsynth estimations were deliverable.
%   ==> Thus, we have unbiase estimations for 321 of 405 fu units (79%)

% Some stats:
%
%
%
%
%

\newpage
% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\subsection{Estimation errors}
\label{sec:esterr}

On both small area levels, the design-unbiased estimators \psmall{} and \extpsynth{} led to a substantial reduction in the estimation errors compared to the SRS estimator (fig. \ref{fig:disterrors}). On the FA level, the SRS estimator yielded an estimation error of 6.7\% on average compared to 5.2\% and 4.8\% under the \extpsynth{} and \psmall{} estimator. The cumulative error distribution (fig. \ref{fig:disterrors}, left) reveals that under the SRS estimator, errors $\leq$ 5\% were achieved for 17\% of the FA units (8 of 45). This proportion could be increased to 62\% (28 FA units) and 73\% (33 FA units) by application of \psmall{} and \extpsynth{}. 95\% of all estimates exhibited errors $\leq$ 9.5\% under the SRS estimator and $\leq$ 6.6\% when using \psmall{} or \extpsynth{}. Estimation errors higher than 10\% only appeared twice for each of the unbiased estimators.\par

The error reduction by the unbiased double sampling estimators was even more pronounced on the FR level (fig. \ref{fig:disterrors}, right), although the overall error niveau was substantially higher than on FA level. The average error under the SRS estimator was 18.3\%, while it was 11.3\% and 12.2\% under the \psmall{} and \extpsynth{} estimator. 95\% of the 321 FR units where \psmall{} and \extpsynth{} could be applied exhibited errors $\leq$ 20\%. In comparion, the SRS estimates resulted in errors $\leq$ 36.6\% for 95\% of the 388 FR units and exceeded an error of 20\% in 30\% of the cases.\par

@@

% Whereas the estimation errors under PSMALL and PSYNTH were limited to maximum of 41 and 45\%, The SRS estimates exceeded this value in 11 FR units.
%
% AS obvious from figure \ref{fig:disterrors} (right), the major improvement 
%
%
%
%
% The PSYNTH estimator always resulted in much smaller estiamtion errors compared to PSMALL and PSYNTH. This is because ...
%
% As obvious from figure \ref{fig:disterrors}, the error distribution of PSMALL and EXTPSYNTH were found to be very similar and suggested that the two estimator performed very similar. In section \ref{sec:comp}, we analysed the differences between the two estimators in more detail.
%
%The highest observed estimation error was 14\% for the SRS, PSMALL and EXTPSYNTH estimator.

\newpage
% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\subsection{Comparison of \psmall{} and \extpsynth{}}
\label{sec:comp}

As obvious from figure \ref{fig:disterrors}, the error distribution of \psmall{} and \extpsynth{} were found to be very similar, with \psmall{} showing marginally higher estimation errors. In order to investigate the differences between \psmall{} and \extpsynth{}, we compared the g-weight variances of both estimators for all 321 FR units (fig. \ref{fig:compvar}, left). As obvious, \psmall{} yielded slightly larger variances for the vast majority of the estimates. As addressed in section \ref{sec:extpsynth}, one possible explanation for such differences was the effect of one or more cluster not entirely being included in a small area unit, as this would constitute a violation of the \extpsynth{} estimator. This violation was actually observed in 155 of the 321 FR units (48\%). However, the affected FR units (depicted in red color, fig. \ref{fig:compvar}) did not show a significant divergence from the \psmall{} variances with respect to the remaining unaffected FR units. The variance differences between the two estimators were expected to occur for the following reason: as depicted in \citet[pp.17--18]{mandallaz2016}, the mathematical formulations of the \psmall{} and \extpsynth{} estimator are asymptotically equivalent only under large terrestrial sample sizes $n_{2,G}$ within the small area. An additional comparison of the absolute differences in the g-weight variance (fig. \ref{fig:compvar}, right) revealed that large differences did in fact particularly occur for small area units with small terrestrial sample sizes ($n_{2,G} \leq 5$). The differences decreased with increasing sample size and thus confirmed the asymptotic relationship between the two estimators. However, a comparison of the confidence intervals of \psmall{} and \extpsynth{} revealed that the variance differences did not lead to statistically significant point estimates.\par

%As obvious from figure \ref{fig:disterrors}, the error distribution of \psmall{} and \extpsynth{} were found to be very similar, with \psmall{} showing marginally higher estimation errors. Differences between the two estimators were expected to occur for the following reasons: 1) as depicted in \citet[pp.17--18]{mandallaz2016}, the mathematical formulations of the \psmall{} and \extpsynth{} estimator are asymptotically equivalent only under large terrestrial sample sizes $n_{2,G}$ within the small area. Therefore, differences between the estimators were particularly expected for small area units with low terrestrial sampling intensities. 2) As addressed in section \ref{sec:extpsynth}, the case of one or more cluster not entirely being included in a small area unit would constitute a violation of the \extpsynth{} estimator. Effects of this violation on the estimates had yet not been investigated and also lead to a divergence between \psmall{} and \extpsynth{}.\par
%
%In order to investigate the differences between \psmall{} and \extpsynth{}, we compared the g-weight variances of both estimators for all 321 FR units (fig. \ref{fig:compvar}, left). As obvious, \psmall{} yielded slightly larger variances for the vast majority of the estimates. A violation of the \extpsynth{} assumption by one or more cluster not entirely included in a small area unit was observed in 155 of the 312 FR units (48\%). However, the affected FR units (depicted in red color, fig. \ref{fig:compvar}) did not show a significant divergence from the \psmall{} variances with respect to the remaining unaffected FR units. An additional comparison of the absolute differences in the g-weight variance (fig. \ref{fig:compvar}, right) revealed that large differences particularly occurred for small area units with small terrestrial sample sizes ($n_{2,G} \leq 5$). The differences decreased with increasing sample size and thus confirmed the asymptotic relationship between the two estimators. A comparison of the confidence intervals of \psmall{} and \extpsynth{} revealed that the variance differences did not lead to statistically significant point estimates.\par

@@

\newpage
% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\subsection{Reduction of variance by two-phase estimators}
% \subsection{Variance reduction of SRS estimator}
\label{sec:gain_eval}

@@

@@

%% NOTES:
% - 
%
%
%
%
%
%
%

>>>>

An application of the SRS, \psmall{} and \extpsynth{} estimator was not feasible for 17 of all 405 FR-units due to an insufficient terrestrial sample size of $n_{2,G} < 2$. We further restricted the calculation of \psmall{} and \extpsynth{} to small area units with a minimum terrestrial sample size of $n_{2,G} \geq 4$ to avoid unstable estimates. This affected 65 additional FR units and limited unbiased two-phase estimations to 321 (79\%) of the 405 FR units. It should be noted that also the \psynth{} estimator could not be applied for 2 FR-units since $n_{1,G} < 1$. Due to substantial larger sample sizes, all estimators could however be applied in all small area units on the FA level. The average value and the range of the mean timber volume estimates over the evaluated FA and FR units turned out to be very similar between all estimators (table \ref{tab:estres}). An additional pairwise comparison of the 95\% confidence intervals for all FA- and FR-units revealed that the four estimators did in fact not produce statistically different point estimates. This confirmed that the differences between the estimators are solely found in the precision which they provide for the point estimates.

%% NOTES
%
% Feasibility: 
% FA-level: for 44 out of 45 FA-units, the full model could be applied. For one remaining, only the model without tree species was applied.
% 
% FR-level: 
% o mathemat. feasibility:
%    - op-estimation feasible for 388 of the 405 fu-units. --> for 17 fus not possible due to n2G < 2
%    - psmall / extpsynth possible for 388 of the 405 units (for 17 fus not possible). Reason: n2G < 2 (identical with op)
%    - psynth not possible for 403 of 405. For 2 units not possible due to n1G < 2 (these two are included in the 19 above).
%    -> basically, for these 2 fu-units, none of the estimators could produce estimations due to n1G < 2
%  o restriction of unbiased estimtors to n2G >= 4: 
%    - psmall / extpsynth: 65 of the 386 fu-units have n2G < 4, so theyx cancel out. Thus we have 19 + 65 = 84 fu-units for which no psmall & extpsynth estimations were deliverable.
%       ==> Thus, we have unbiase estimations for 321 of 405 fu units (79%)

% Mention: a comparison of the confidence intervals between revealed that the

\begin{table}[H]
	\begin{center}
		\caption{Descriptive summary of point estimates and estimation errors on the two forest district levels. $N_u$: number of evaluated small area units.}
		\vspace{0.2cm}
		\label{tab:estres}
		{\small %
			\begin{tabular}{c|l c|c|c|c|c|c|c} %8cols
				\hlineB{1}
				\multirow{2}{*}{District level} & \multicolumn{2}{c|}{\multirow{2}{*}{Estimator}} & \multicolumn{3}{c|}{Point estimates} & \multicolumn{3}{c}{Errors [\%]} \\
				\cline{4-9} & & & mean & min & max & mean & min & max \\
				\hline \hline
				\multirow{4}{*}{FA} & SRS       & ($N_u$=45)  & 300.16 & 215.91 & 392.84 &  6.69 & 3.87 & 13.21 \\
				                    & PSMALL    & ($N_u$=45)  & 307.29 & 209.26 & 417.10 &  5.16 & 3.46 & 14.33 \\
				                    & EXTPSYNTH & ($N_u$=45)  & 307.27 & 209.01 & 415.02 &  4.78 & 3.25 & 13.88 \\
				                    & PSYNTH    & ($N_u$=45)  & 306.90 & 223.51 & 409.92 &  2.34 & 1.54 &  3.95 \\
				\hlineB{2}          
				\multirow{4}{*}{FR} & SRS       & ($N_u$=388) & 301.83 &  99.89 & 612.13 & 18.32 & 0.34 & 104.97 \\
				                    & PSMALL    & ($N_u$=321) & 308.15 & 159.64 & 568.67 & 12.24 & 3.48 &  44.94 \\
				                    & EXTPSYNTH & ($N_u$=321) & 308.38 & 154.07 & 544.34 & 11.34 & 3.60 &  40.91 \\
				                    & PSYNTH    & ($N_u$=403) & 307.82 & 166.01 & 444.29 & 4.65  & 2.56 &  62.51 \\
				\hline \hline
			\end{tabular}
		}%
	\end{center}
\end{table}

% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\subsection{Estimation errors}
\label{sec:esterr}

On both small area levels, the design-unbiased estimators \psmall{} and \extpsynth{} led to a substantial reduction in the estimation errors compared to the SRS estimator (fig. \ref{fig:disterrors}). On the FA level, the SRS estimator yielded an estimation error of 6.7\% on average compared to 5.2\% and 4.8\% under the \extpsynth{} and \psmall{} estimator (table \ref{tab:estres}). The cumulative error distribution (fig. \ref{fig:disterrors}, left) reveals that under the SRS estimator, errors $\leq$ 5\% were achieved for 17\% of the FA units (8 of 45). This proportion could be increased to 62\% (28 FA units) and 73\% (33 FA units) by application of \psmall{} and \extpsynth{}. 95\% of all estimates exhibited errors $\leq$ 9.5\% under the SRS estimator and $\leq$ 6.6\% when using \psmall{} or \extpsynth{}. Estimation errors higher than 10\% only appeared twice for each of the unbiased estimators.\par
The error reduction by the unbiased double sampling estimators was even more pronounced on the FR level (fig. \ref{fig:disterrors}, right), although the overall error niveau was substantially higher than on FA level. The average error under the SRS estimator was 18.3\%, while it was 11.3\% and 12.2\% under the \psmall{} and \extpsynth{} estimator (table \ref{tab:estres}). Errors smaller than 10\% were achieved in 15\% by the SRS estimator and 46\% by the \psmall{} and \psynth{} estimator. 95\% of the 321 FR units where \psmall{} and \extpsynth{} could be applied exhibited errors $\leq$ 20\%. In comparion, the SRS estimates resulted in errors $\leq$ 36.6\% for 95\% of the 388 FR units.

@@

% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\subsection{Comparison of \psmall{} and \extpsynth{}}
\label{sec:comp}

Figure \ref{fig:disterrors} revealed that the error distribution of \psmall{} and \extpsynth{} are very similar, with \psmall{} showing marginally higher estimation errors. In order to investigate the differences between \psmall{} and \extpsynth{}, we compared the g-weight variances of both estimators for all 321 FR units (fig. \ref{fig:compvar}, left). As obvious, \psmall{} yielded slightly larger variances for the vast majority of the estimates. As addressed in section \ref{sec:extpsynth}, one possible explanation for such differences was the effect of one or more cluster not entirely being included in a small area unit, as this would constitute a violation of the \extpsynth{} estimator. This violation was actually observed in 155 of the 321 FR units (48\%). However, the affected FR units (depicted in red color, fig. \ref{fig:compvar}) did not show a significant divergence from the \psmall{} variances with respect to the remaining unaffected FR units. The variance differences between the two estimators were expected to occur for the following reason: as depicted in \citet[pp.17--18]{mandallaz2016}, the mathematical formulations of the \psmall{} and \extpsynth{} estimator are asymptotically equivalent only under large terrestrial sample sizes $n_{2,G}$ within the small area. An additional comparison of the absolute differences in the g-weight variance (fig. \ref{fig:compvar}, right) revealed that large differences did in fact particularly occur for small area units with small terrestrial sample sizes ($n_{2,G} \leq 5$). The differences decreased with increasing sample size and thus confirmed the asymptotic relationship between the two estimators. However, a comparison of the confidence intervals of \psmall{} and \extpsynth{} revealed that the variance differences did not lead to statistically significant point estimates.\par

@@

% \newpage
% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\subsection{Reduction of SRS variance by \psmall{} and \extpsynth{}}
\label{sec:gain_eval}

We further evaluated how much the variance of the SRS estimator in each FA and FR unit was reduced by alternative application of the \psmall{} and \extpsynth{} estimator. For all FA-units, the application of \psmall{} and \extpsynth{} led to a reduction of the SRS variance that was up to 54.1\% and 49.7\% in 75\% of the FA-units (fig. \ref{fig:gain}). The differences between \psmall{} and \extpsynth{} were again due to the slightly smaller variances produced by the \extpsynth{} estimator. The reduction in variance was also expressed in the relative efficiency, which was 2.02 on average and ranged between 1.18 and 4.13 for the \extpsynth{} estimator. On FR-level, the achieved reduction in variance and the relative efficiencies reached even higher values than on FA-level (table \ref{tab:gain}). However, cases also occurred where one or both two-phase estimators produced partly substantially larger variance values than under the SRS estimator. This particularly happened in 18\% (61) of the FR-units under the \extpsynth{}, and in 23\% (76) of the FR-units under the \psmall{} estimator.

@@

\begin{table}[H]
	\begin{center}
		\caption{Descriptive summary of SRS variance reduction and relative efficiencies on the two forest district levels. $N_u$: number of evaluated small area units.}
		\vspace{0.2cm}
		\label{tab:gain}
		{\small %
			\begin{tabular}{c|l c|c|c|c|c|c|c} %8cols
				\hlineB{1}
				\multirow{2}{*}{District level} & \multicolumn{2}{c|}{\multirow{2}{*}{Estimator}} & \multicolumn{3}{c|}{Reduction of SRS variance [\%]} & \multicolumn{3}{c}{relative efficiency} \\
				\cline{4-9} & & & mean & min & max & mean & min & max \\
				\hline \hline
				\multirow{2}{*}{FA} & PSMALL    & ($N_u$=45)  & 33.51 & 0 & 72.5 & 1.74 & 1.03 & 3.64 \\
				& EXTPSYNTH & ($N_u$=45)  & 43.30 & 0 & 75.8 & 2.03  & 1.18 & 4.13 \\
				\hlineB{2}          
				\multirow{2}{*}{FR} & PSMALL    & ($N_u$=321) & 12.48 & 0 & 96.8 & 2.54 & 0.08 & 31.61  \\
				& EXTPSYNTH & ($N_u$=321) & 24.75 & 0 & 97.0 & 2.95 & 0.10 & 33.70 \\
				\hline \hline
			\end{tabular}
		}%
	\end{center}
\end{table}

Here comes some detective work ...

@@
